\section{Conclusion}

We presented \OurBench, an execution-based benchmark that evaluates autonomous coding agents on improving Core Web Vitals for real websites sourced from production GitHub repositories. The benchmark comprises 2{,}741 repositories across 17 frameworks, evaluated through a containerized harness that deploys each site, measures CWV in a real browser, and enforces Pareto improvement across six metric-device combinations.

Evaluation of eleven agent-LLM configurations reveals that the best system (OpenCode + GPT-5.1\,Codex) achieves Pareto improvement on 56.7\% of sites, while the worst (OpenCode + GPT-4.1) degrades 90\% of sites. Controlled ablations separate two factors: the agent scaffold governs whether the system can structure multi-metric trade-offs (a 16$\times$ Pareto-rate gap across frameworks at fixed model), while the underlying LLM determines whether the plan executes without collateral regressions. Qualitative analysis shows that successful agents make surgical, targeted edits to a small number of files, while failing agents scatter modifications broadly or apply template optimizations without regard for existing metric health.

Three findings have implications beyond web performance. First, multi-metric Pareto scoring exposes failure modes that single-metric benchmarks miss: agents that improve LCP while degrading CLS or INP appear successful under any individual metric but fail the joint criterion. Second, no agent in our evaluation produces an empty patch for an already-optimal site, suggesting that current systems lack calibrated restraint. Third, the continuous-reward structure of CWV measurement supports reinforcement learning with verifiable rewards for training software engineering agents, which we leave to future work. Extending the benchmark to full-stack applications with server-side rendering, incorporating iterative multi-round optimization, and studying the ``do nothing'' policy for healthy sites are open directions. The refresh pipeline enables continuous incorporation of new repositories to keep pace with evolving web development practices.
