\section{Background and Methodology}

\label{sec:background_cwv} 
\subsection{Core Web Vitals}
Core Web Vitals (CWVs) are standardized, user-centric performance metrics that quantify web experience along three dimensions: \textbf{Largest Contentful Paint (LCP)}, measuring perceived load speed; \textbf{Cumulative Layout Shift (CLS)}, measuring visual stability; and \textbf{Interaction to Next Paint (INP)}, measuring responsiveness.\footnote{\url{https://web.dev/vitals/}} Google rates LCP under 2.5\,s, CLS below 0.1, and INP under 200\,ms as ``good.'' In this work, the \emph{unit of evaluation is a webpage}: a single URL whose CWVs are measured end-to-end in a browser. A \emph{website} (repository) contributes multiple webpages (the homepage plus a bounded set of internal pages), enabling evaluation across heterogeneous page templates. The three metrics interact --- deferring JavaScript may improve INP but delay LCP --- so evaluation must be multi-metric.

\subsection{\OurBench}
\label{sec:bench_sources}

\OurBench is an execution-based benchmark for evaluating coding agents on \emph{goal-directed website performance optimization}. Each benchmark instance consists of a pinned repository snapshot, a deterministic localhost deployment script, and a set of evaluation webpages. Agents may freely modify the repository and succeed by improving CWVs under strict non-regression constraints, rather than matching a reference patch. The final benchmark contains 2{,}741 repositories and 73K deduplicated webpages spanning 17 frameworks, sourced from \textbf{GH-25}~\cite{nick007x_github_code_2025} (a 2025 snapshot of 1.5M GitHub repositories) and \textbf{Stack (dedup-v2)}~\cite{Kocetkov2022TheStack} (an archival corpus of 60M+ repositories). Figure~\ref{fig:curation_pipeline} illustrates the full pipeline.

\paragraph{Repository curation.}
We construct benchmark candidates through a three-stage filtering pipeline (Figure~\ref{fig:gh25_filtering_pipeline}). First, \emph{structural filtering} retains repositories whose file layout resembles a web project (framework configs, deployment files, web assets) while removing empty, backend-only, or library-only repositories. Second, \emph{content verification} examines package manifests, READMEs, and root HTML to confirm a real web stack and assign a framework label via deterministic heuristic scripts (Appendix~\ref{tab:framework-detection-heuristics}). Third, \emph{public-website association} links each repository to its live homepage via the GitHub About field, deduplicates by URL, and discards repositories without a reachable site (94\% precision in a 100-site manual audit). Quality filters require $\geq$10 files, $\geq$100KB total size, no forks, and $>$75\% web-language files. Each surviving repository is assigned a deterministic deployment script, deployed locally, and validated against its live GitHub Pages rendering using visual, DOM, and content similarity checks; failures are discarded (Appendix~\ref{subsection:build_commands}). Of the 8{,}043 GH-25 candidates, ${\sim}$3.5K have CrUX field data; the pipeline yields ${\sim}$670 new candidates per month (${\sim}$280 with CrUX), providing natural contamination resistance through continuous refresh.

\paragraph{Webpage expansion.}
We expand each site beyond its homepage by recursively discovering internal pages via sitemaps, in-page links, and source HTML files. Regex-based URL deduplication and DOM-based near-duplicate removal yield 73K diverse webpages across the benchmark (Appendix~\ref{app:page_dedup}). Each instance is pinned to a commit hash and verification timestamp to ensure reproducibility.

\begin{table}[t]
\centering
\small
\begin{tabular}{lcc}
\hline
 & \textbf{Full benchmark} & \textbf{Eval subset} \\
\hline
Repositories & 2{,}741 & 298 \\
Stack / GH-25 & 2453 / 278& 275 / 23\\
Files (p50 / p90) & 334 / 2{,}718 & 771 / 10{,}533 \\
Lines of Code (median / p90) & 121K/ 1.08M & 129K / 3.1M \\
\hline
\end{tabular}
\caption{\OurBench Statistics: The full benchmark contains 2,741 pinned GitHub Pages repositories and 73k deduplicated internal webpages. We evaluate agents on a stratified subset of 500 WebPages.}
\label{tab:bench_stats}
\end{table}

\subsection{Developer Effort Mining.}
Beyond measuring whether repositories can be improved, we also ask how much observable developer effort real-world performance improvements usually require. For this analysis, we start from commits that were already identified as related to Lighthouse, Core Web Vitals, PageSpeed, or web performance improvements. However, a single commit is often too small a unit to represent effort: the actual work may include code changes, review, discussion, testing, and integration. Therefore, we reconstruct the pull requests associated with these performance-related commits and treat each pull request as the main unit of effort.

For each performance-related commit, we identify the corresponding GitHub pull request using repository metadata and validated pull-request references in commit messages. This gives us a PR-level view of the work surrounding the performance change. We then collect simple, interpretable effort signals for each pull request: how long the PR remained open, how many commits it contained, how many files it changed, how many lines were added or deleted, and how much discussion occurred through comments or reviews. Pull requests open for less than one hour are excluded from the main analysis because they are likely to be empty, accidental, automated, or very small administrative changes. Importantly, we do not claim to measure exact human working hours. Instead, we measure observable engineering effort as reflected in the public pull-request lifecycle.

\paragraph{Results.}
Our effort-mining pipeline recovered detailed metadata for \textbf{2,237} pull requests associated with CWV/Lighthouse-related commits. Of these, \textbf{750} pull requests were open for less than one hour and were excluded from the main analysis. This leaves \textbf{1,487 non-trivial performance-related pull requests} for measuring developer effort.

The median performance-related pull request remained open for \textbf{59.69 hours}, or approximately \textbf{2.49 days}. This shows that real-world performance improvements are usually not instantaneous one-line changes. Even when the performance signal appears in a small number of commits, the surrounding pull-request lifecycle often spans multiple days. The distribution is also strongly right-skewed: the 75th percentile is \textbf{10.50 days}, the 90th percentile is \textbf{36.13 days}, and the 95th percentile is \textbf{65.23 days}. Thus, while many performance fixes are completed quickly, a meaningful fraction remain open for weeks, likely reflecting review delays, integration complexity, testing requirements, or coordination with broader development work.

In terms of speed of completion, \textbf{37.12\%} of non-trivial performance pull requests were completed within the same day. However, \textbf{30.26\%} remained open for more than one week, and \textbf{20.44\%} remained open for more than two weeks. This suggests that performance work has a heavy-tailed effort profile: many changes are small and quickly merged, but a substantial minority require prolonged engineering and review cycles.

The code-change statistics show a similar pattern. The median pull request contained \textbf{4 commits}, but only \textbf{1 commit} was directly identified as CWV/Lighthouse-related. This indicates that performance improvements are often embedded inside broader maintenance or implementation work rather than appearing as isolated performance-only patches. The median PR modified \textbf{5 files}, with a median churn of \textbf{155 additions} and \textbf{34 deletions}. The median PR also had \textbf{2 comments}, while the median number of formal review comments was \textbf{0}. This suggests that many performance-related changes involve at least some visible coordination, but not all require extensive formal code-review discussion.

\begin{table}[t]
\centering
\small
\begin{tabular}{lr}
\toprule
\textbf{Effort signal} & \textbf{Value} \\
\midrule
Total PRs with detailed metadata & 2,237 \\
PRs excluded as $<$1 hour & 750 \\
Main non-trivial PRs analyzed & 1,487 \\
Median PR open duration & 59.69 hours / 2.49 days \\
75th percentile PR duration & 10.50 days \\
90th percentile PR duration & 36.13 days \\
95th percentile PR duration & 65.23 days \\
Same-day PRs & 37.12\% \\
PRs open $>$7 days & 30.26\% \\
PRs open $>$14 days & 20.44\% \\
Median commits per PR & 4 \\
Median CWV/Lighthouse-related commits per PR & 1 \\
Median changed files per PR & 5 \\
Median additions per PR & 155 \\
Median deletions per PR & 34 \\
Median comments per PR & 2 \\
Median review comments per PR & 0 \\
\bottomrule
\end{tabular}
\caption{Observable developer-effort signals for CWV/Lighthouse-related pull requests. PR open duration is measured from pull-request creation to merge or closure. PRs open for less than one hour are excluded from the main analysis.}
\label{tab:developer-effort}
\end{table}

\paragraph{Interpretation.}
These results show that improving real-world web performance requires measurable developer effort. The median PR duration of \textbf{2.49 days} indicates that a typical non-trivial CWV/Lighthouse-related improvement takes more than a quick commit-and-merge cycle. At the same time, the long upper tail shows that performance work can become substantially more involved: roughly one in five non-trivial PRs remains open for more than two weeks. This is important for understanding the practical value of \OurBench. The benchmark is not only testing whether an agent can make a syntactic code edit; it targets tasks that correspond to real developer workflows with observable review, integration, and maintenance effort. Performance improvements may look small in isolation, but the PR-level evidence shows that they often require multi-day engineering work across multiple files and commits.
\subsection{CWV Evaluation Harness}
\label{sec:cwv-evaluation}
Each evaluation instance runs in a containerized environment that deploys the repository to localhost, measures CWVs under mobile and desktop profiles, and enforces anti-regression checks (Figure~\ref{fig:evaluation_harness}).

\paragraph{Deployment and measurement.}
The harness checks out the pinned commit in a Docker container, installs dependencies, and serves the site on localhost (max build time: 3 minutes). A headless Chromium browser via Playwright injects Web Vitals instrumentation (PerformanceObserver hooks for LCP, CLS, INP, FCP, TTFB, FID) and performs controlled interactions (scroll, click, type) to elicit INP/FID. Full instrumentation details are in Appendix~\ref{lst:cwv-injection}.

\paragraph{Aggregation and device profiles.}
For each (site, device) pair, we perform 30 independent runs with fresh browser contexts, apply IQR-based outlier removal, and report p75 aggregates. Mobile and desktop profiles specify distinct viewport, CPU throttling, and network shaping parameters (Appendix~\ref{app:hyperparams}).

\paragraph{Regression checks and validation.}
Before scoring, we enforce four checks: (i) visual consistency via GPT-4.1-based screenshot comparison, (ii) DOM consistency via locality-sensitive hashing, (iii) content consistency (Jaccard $\geq$ 0.97), and (iv) no new console errors. Build failures or failed checks invalidate the attempt (Appendix~\ref{app:regression}). Lab-field validation against CrUX yields a Spearman rank correlation of \textbf{0.87}, confirming that relative site orderings in our harness mirror real-world performance.



\subsection{Agent Benchmarking Protocol}
\label{sec:agent_protocol}
For each task, the agent is provided with: (i) the full repository snapshot, (ii) the deterministic host script for localhost deployment, (iii) baseline CWV scores for mobile and desktop, and (iv) diagnostic attribution signals including candidate LCP elements and elements associated with CLS/INP events. Agents interact with the environment via standard development tools (file editing and shell commands).

\paragraph{Budgets, logging, and retries}
Each task is allocated a maximum wall-clock time of 15 minutes and up to 25 model interaction steps. We log all model messages, tool invocations, patches, deployment logs, measurement artifacts, and regression-check outcomes. We allow up to 3 retries for transient deployment or measurement failures; invalid attempts due to regressions or build errors are not retried beyond this budget. These settings ensure that evaluation captures both effectiveness and robustness under realistic constraints (Appendix~\ref{app:logging}).

\paragraph{Evaluation Loop}
\label{sec:eval_loop}
The generated patch is then applied to the codebase in a new branch, this branch is re-evaluated for CWVs as discussed in listing \ref{sec:cwv-injection} and if it passes the regressions, it is considered a valid attempt. Figure \ref{fig:evaluation_harness} shows the overall flow.