\section{Additional Related Work}

\paragraph{Coding-agent benchmarks.}
Evaluation of coding agents has progressed from function-level synthesis \citep{chen2021codex,austin2021programsynthesislargelanguage} to repository-level issue resolution. SWE-bench \citep{jimenez2024swebenchlanguagemodelsresolve} and its derivatives (Verified, M, Pro \cite{deng2025swe}, SWE-smith, SWE-rebench) evaluate whether agents can resolve GitHub issues against unit tests on Python repositories. SWE-EVO \cite{thai2025swe} extends this to multi-change software evolution scenarios, and SWE-Lancer \cite{miserendino2025swe} evaluates agents on real freelance tasks valued at over \$1M. RepoBench \cite{liu2023repobench}, ExecRepoBench \cite{yang2024execrepobench}, and ProjectEval \cite{liu2025projecteval} benchmark repo-level completion and multi-step project development. All of these benchmarks measure functional correctness via test-suite pass rates. \OurBench evaluates a different property entirely: user-facing browser-measured performance on web repositories spanning JavaScript, TypeScript, HTML, and CSS.

\paragraph{Non-functional and performance benchmarks.}
A smaller body of work evaluates non-functional properties of generated or modified code. GSO \cite{XXX_gso} evaluates runtime speed optimization on systems codebases, using performance tests derived from developer commit histories as specifications. SWE-fficiency \cite{XXX_swefficiency} similarly derives optimization tasks from performance-related pull requests in Python data-science libraries (pandas, NumPy), measuring speedup ratios against the original developer's optimization. Both measure computational throughput via test execution rather than browser-level user experience. BaxBench \cite{XXX_baxbench} evaluates correctness and security of LLM-generated backends across 392 tasks and 14 frameworks, but agents generate applications from scratch rather than optimizing existing repositories. EffiBench \cite{huang2024effibench} and COMPASS \cite{meaden2025compass} measure runtime efficiency and code quality on isolated competitive-programming problems, not real codebases. \OurBench differs from all of these along two axes: the measurement modality is a real browser rendering a hosted site (not a performance test or static analyzer), and the success criterion requires multi-metric Pareto improvement rather than single-metric speedup.

\paragraph{Web-specific benchmarks.}
Several benchmarks target web development. WebSight \cite{bhathal2025websight} and Design2Code \cite{si2025design2code} evaluate screenshot-to-code generation, measuring visual fidelity against reference designs. Web2Code \cite{yun2024web2code} evaluates pixel-level similarity for webpage generation. FrontendBench \cite{zhu2025frontendbench} and Web-Bench \cite{xu2025web} move closer to execution-based evaluation by integrating browser automation (Playwright, Puppeteer) for DOM, layout, and interactivity validation. However, all of these benchmarks evaluate whether generated code \emph{looks and functions correctly}, not whether it \emph{performs well for the user}. None measures loading speed, visual stability, or responsiveness as objective signals. \OurBench fills this gap: agents edit existing production repositories, and the evaluation signal is a browser-measured CWV outcome on a deployed site.
